Sound and Automated Synthesis of Digital Controllers for Continuous Plants

### 2017-03-14 slides/presentation.tex
fixes to slides

\usepackage{url}           % format URLs
\usepackage{listings}      % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
%\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}
%\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb,amsmath,amsfonts} 
\usepackage{mathtools}
\usepackage{microtype}

@@

\renewcommand{\baselinestretch}{0.991}
\allowdisplaybreaks
\newcommand\tool{{\sf DSSynth}\xspace}
\newcommand{\xmark}{\ding{55}}

@@

%\only<2-3>{
%\begin{displaymath}
%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\tilde{C}(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\tilde{C}(z)\hat{Y}(z)
%\end{displaymath}
%}

\only<5>{
\begin{equation*}
\hat{Y}(z) = 
\frac{\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}R(z) + 
\frac{1}{1+\hat{G}(z) \tilde{C}(z)} \nu_{1}(z) + 
\frac{\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)} \nu_{2}(z) 
\end{equation*}
}

\uncover<6>{
Common denominator:
$$\hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z)$$ 
\textcolor{red}{clarify use of tilde C and of hat C }
}

@@

\begin{equation*}
S(z) = \hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z) = \sum_{i=0}^{N_S} c_iz^{N_s-i}, c_0 \neq 0 
\end{equation*}

@@

\textcolor{red}{Introduce details of case study. }

@@

   \only<1,22>{\path (verif2) edge node {} (done);}
   \only<1>{\path ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north);}
   \only<2-7,16-17>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$} ([xshift=5em]gp.north);}
   \only<1-2,8,16,18>{\path ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);}
   \only<3-7,17>{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=-5em]synth.south);}
   \only<1-3,8-9,16,18>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west);}
   \only<4-7,17>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([yshift=2em]verif1.west);}
   \only<1-4,8-10,16,18-19>{\path  ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north);}
   \only<5-7,17>{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=5em]bmc.north);}
   \only<1-5,8-11,16,18-19>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south);}
   \only<6-7>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=-5em]verif1.south);}
   \only<1-6,8-12,16,18>{\path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);}
   \only<7>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([yshift=-2em]synth.east);}
   \only<8-15>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=5em]gp.north);}
   \only<9-15,19->{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\tilde C(z)}$} ([xshift=-5em]synth.south);}
   \only<10-15>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}}$} ([yshift=2em]verif1.west);}
   \only<11-15,20->{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\tilde C(z)}$} ([xshift=5em]bmc.north);}
   \only<12-15,20->{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {\textcolor{blue}{UNSAT}\\\textcolor{blue}{Pass}} ([xshift=-5em]verif1.south);}
   \only<1-12,16-20>{\path ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north);}
   \only<13-15,21->{\path ([xshift=5em]verif2.south) edge node[align=center] {$\textcolor{blue}{\tilde C(z)}$} ([xshift=5em]fp.north);}
   \only<1-13,16-20>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south);}
   \only<14-15>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{False}} ([xshift=-5em]verif2.south);}
   \only<15>{\path ([yshift=-2em]verif1.west) edge node {\textcolor{blue}{precision}} ([yshift=-2em]synth.east);}
   \only<17>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=-5em]verif1.south);}
   \only<17>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([yshift=-2em]synth.east);}
   \only<18->{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=5em]gp.north);}
   \only<19->{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}}$} ([yshift=2em]verif1.west);}
   \only<21->{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{True}} ([xshift=-5em]verif2.south);}

   \path (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
   ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);

 \end{tikzpicture}
}
\end{figure}
\end{frame}

@@

\begin{frame}{Conclusions}
\begin{itemize}
\item We have presented a method for automatically synthesizing stable and sound controllers, implemented
in a tool called \tool.
\item \tool marks the first use of the
CEGIS that handles plants with uncertain models and FWL effects over the
digital controller.  
\item Our experimental results show that \tool is able to synthesize
stable controllers for most benchmarks within a reasonable amount of time.  
\item Future work will extend this CEGIS-based
approach to LTI systems with state space safety specifications. 
\end{itemize}
\end{frame}
\end{document}

>>>>

\usepackage{url}           % format URLs
\usepackage{listings}      % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
%\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}
%\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb,amsmath,amsfonts} 
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{epstopdf}

@@

\renewcommand{\baselinestretch}{0.991}
\allowdisplaybreaks
\newcommand\tool{{\sf DSSynth}\xspace}
\newcommand{\xmark}{\ding{55}}
\newcommand{\mat}[1]{\boldsymbol{#1}}
\newcommand{\cavslides}[1]{#1}

@@

%\only<2-3>{
%\begin{displaymath}
%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\hat{C}(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\hat{C}(z)\hat{Y}(z)
%\end{displaymath}
%}

\only<5>{
\begin{equation*}
\hat{Y}(z) = 
\frac{\hat{G}(z) \hat{C}(z)}{1+\hat{G}(z) \hat{C}(z)}R(z) + 
\frac{1}{1+\hat{G}(z) \hat{C}(z)} \nu_{1}(z) + 
\frac{\hat{G}(z)}{1+\hat{G}(z) \hat{C}(z)} \nu_{2}(z) 
\end{equation*}
}

\uncover<6>{
Common denominator:
$$\hat{G}_n(z) \hat{C}_n(z)+\hat{G}_d(z) \hat{C}_d(z)$$ 
}

@@

\begin{equation*}
S(z) = \hat{G}_n(z) \hat{C}_n(z)+\hat{G}_d(z) \hat{C}_d(z) = \sum_{i=0}^{N_S} c_iz^{N_s-i}, c_0 \neq 0 
\end{equation*}

@@

Take a classical cruise control example from the literature. 
%
\begin{equation*}
G(z) = \frac{0.0264}{z-0.9998}.
\end{equation*}

Using an optimization tool, the following stable high-performance
controller was designed:
%
\begin{equation*}
C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation*}
%
However, if we implement the controller in $\mathbb{R} \langle 4,16\rangle$.
%
\begin{equation*}
\resizebox{.9\textwidth}{!}{
$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
}
\end{equation*} 
%
where $\tilde{C}(z)$ is the controller adjusted to the FWL. The resulting system is unstable.

@@

   \only<1,22>{\path (verif2) edge node {} (done);}
   \only<1>{\path ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north);}
   \only<2-7,16-17>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$} ([xshift=5em]gp.north);}
   \only<1-2,8,16,18>{\path ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);}
   \only<3-7,17>{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=-5em]synth.south);}
   \only<1-3,8-9,16,18>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west);}
   \only<4-7,17>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([yshift=2em]verif1.west);}
   \only<1-4,8-10,16,18-19>{\path  ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north);}
   \only<5-7,17>{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=5em]bmc.north);}
   \only<1-5,8-11,16,18-19>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south);}
   \only<6-7>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=-5em]verif1.south);}
   \only<1-6,8-12,16,18-19>{\path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);}
   \only<7>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([yshift=-2em]synth.east);}
   \only<8-15>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=5em]gp.north);}
   \only<9-15,19->{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=-5em]synth.south);}
   \only<10-15>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}}$} ([yshift=2em]verif1.west);}
   \only<11-15,20->{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=5em]bmc.north);}
   \only<12-15,20->{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {\textcolor{blue}{UNSAT}\\\textcolor{blue}{Pass}} ([xshift=-5em]verif1.south);}
   \only<1-12,16-20>{\path ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north);}
   \only<13-15,21->{\path ([xshift=5em]verif2.south) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=5em]fp.north);}
   \only<1-13,16-20>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south);}
   \only<14-15>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{False}} ([xshift=-5em]verif2.south);}
   %\only<15>{\path ([yshift=-2em]verif1.west) edge node {\textcolor{blue}{precision}} ([yshift=-2em]synth.east);}
   \only<17>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=-5em]verif1.south);}
   \only<17>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([yshift=-2em]synth.east);}
   \only<18->{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=5em]gp.north);}
   \only<19->{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}}$} ([yshift=2em]verif1.west);}
   \only<21->{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{True}} ([xshift=-5em]verif2.south);}

   \path (aux1) edge (synth.north);
   \path[-] (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2);
   \only<1-14,16-> {\path[-] ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);}
   \only<15> {\path[-] ([xshift=6.7cm]aux2) edge node[align=center] {\textcolor{blue}{Increase Precision}} (aux1);}
 \end{tikzpicture}
}
\end{figure}
\end{frame}

@@

\begin{frame}{Conclusions}
\begin{itemize}
\item We have presented a method for automatically synthesizing stable and sound controllers, implemented
in a tool called \tool.
\item \tool marks the first use of the
CEGIS that handles plants with uncertain models and FWL effects over the
digital controller.  
\item Our experimental results show that \tool is able to synthesize
stable controllers for most benchmarks within a reasonable amount of time.  
\item Future work will extend this CEGIS-based
approach to LTI systems with state space safety specifications. 
\end{itemize}
\end{frame}

\begin{frame}[fragile]{LTI Closed Loop System}
\begin{figure}[htb]
\centering

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
    \node[draw=none] (r) {$r_k$};

   \& \node[circle,add={-}{+}{\only<3>{+}}{}] (circle) {};
   \only<3>{\node[draw=none] (v12) at ([xshift=0cm,yshift=1cm]circle)  {$\nu_2-\mat{K}_d\nu_1+\nu_3$};}
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-1.5cm]circle)  {\sc $\mat{K}_d$};
   \coordinate (kdsouth) at ([yshift=-2cm]Kd);

\only<1>{
 \& \node[rectangle,draw,minimum width=3cm,
	minimum height=1.6cm,] (bbdac) {\sc DAC};
 }

\only<2>{   
   \& complexnode/.pic={ 
     \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
   }   
}

   \& complexnode/.pic={ 
      \only<1-2>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};}
      \only<3>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.75cm]dac.center) {};}
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2cm,yshift=.5cm]plant.center)  {\sc \only<1-2>{$\mat{B}$}\only<3>{$\mat{B}_d$}};
      \node[draw=none] (u) at ([xshift=-.8cm,yshift=.15cm]B)  {\only<1-2>{$u(t)$}};
      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-0.6cm,yshift=.5cm]plant.center) {};
      \node[draw=none] (xdot) at ([xshift=.9cm,yshift=.2cm]p1)  {\only<1-2>{$\dot{\mat{x}}(t)$}\only<3>{$\mat{x}_{k+1}$}};   
      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=1.2cm,yshift=.5cm]plant.center) {\sc \only<1-2>{$\int$}\only<3>{$Z^{-1}$}};
      \coordinate (xsouth) at ([xshift=1cm]int);
      \node[draw=none] (x) at ([xshift=1.2cm,yshift=.15cm]int)  {\only<1-2>{$\mat{x}(t)$}\only<3>{$\mat{x}_k$}};
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=1.2cm,yshift=-1cm]plant.center)  {\sc \only<1-2>{$\mat{A}$}\only<3>{$\mat{A}_d$}};
      \coordinate (aeast) at ([xshift=1cm]A);
      \coordinate (awest) at ([xshift=-1.8cm]A);
    }

\only<1>{
 \& \node[rectangle,draw,minimum width=3cm,
	minimum height=1.6cm,] (bbadc) {\sc ADC};
     \coordinate (ykeast) at ([xshift=1.9cm]bbadc);
     \coordinate (yksouth) at ([xshift=1.9cm,yshift=-3.5cm]bbadc);
 }
\only<2>{
   \& complexnode/.pic={ 
     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
     \coordinate (switch1) at ([xshift=-1cm]adc.center);
     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\mat{x}_k$};} 
     \coordinate (ykeast) at ([xshift=1.9cm]q1);
     \coordinate (yksouth) at ([xshift=1.9cm,yshift=-3.5cm]q1);
   }
   \& \coordinate (aux1);
   \& \\
  };
\only<3>{
   \coordinate (ykeast) at ([xshift=4.5cm]int);
   \coordinate (yksouth) at ([xshift=4.5cm,yshift=-5.8cm]int);
}
  \path[->] (r) edge (circle.west);
  \only<1>{
  \path
    (circle.east) edge (bbdac.west)
    (bbdac.east) edge (B.west);
  }
  \only<2>{
    \path[->] (v2) edge (q2.south);
    \path[->] (circle.east) edge (q2.west);
    \path       (q2.east) edge (zoh.west);
    \path[->] (zoh.east) edge (B.west);
  }
  \only<3>{
    \path[->] (v12) edge (circle.north);
    \path[->] (circle.east) edge (B.west);
  }
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south);
   \only<2>{
   \path[->] (v1) edge (q1.south);
   \path   
   (int.east) edge (switch1.west)
   (switch2) edge (q1.west);
   }
\only<1>{ 
  \path 
    (int.east) edge (bbadc.west)
    (bbadc.east) edge (ykeast);
}   
\only<2>{ \path (q1.east) edge (ykeast);}
\only<3>{ \path (int.east) edge (ykeast);}
  \path
   (ykeast) edge (yksouth)
   (yksouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
\end{figure}
\uncover<3>{
\begin{align*}
A_d &= e^{A T_s} = \mathcal{L}^{-1} { ( s I - A )^{-1} }_{t = T_s}\\
B_d &= \int_{0}^{T_s} e^{A t} dt\ B = A^{-1} ( A_d - I ) B
\end{align*}}
\end{frame}

\begin{frame}[fragile]{Multi-stage Verification CEGIS}
\begin{figure}[htb]
{\scriptsize
\centering
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=.9cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \coordinate (aux3);
   \& \coordinate (aux4);
   \&;\\
   \coordinate (aux5);
   \& \coordinate (aux6);
   \&;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=6cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc ~~~~~~~~~~~~Verify},] (verif) {};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 2.Safety}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 3.Precision}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 4.Complete}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {\sf Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\Verifier};
   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\Verifier};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$K$} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$K$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$K$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {$K$} ([xshift=5em]sv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    (verif) edge node {PASS} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$K$} ([xshift=-5em]synth.south)
    (aux3) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=0cm]aux6)
   ([xshift=0cm]aux6) edge node[align=center] {Increase Precision} (aux5)
   (verif3.north) edge node[align=center] {} ([xshift=6.7cm]aux4)
   ([xshift=6.7cm]aux4) edge node[align=center] {Increase Unfolding Bound} (aux3);

 \end{tikzpicture}
}}
\end{figure}
\end{frame}

\begin{frame}[fragile]{Completeness Bound}
\begin{figure}[t]
\centering
\includegraphics[width=0.6\textwidth]{ct.eps}
\vspace{0.1cm}
\label{fig:ct}
\end{figure}
\end{frame}

%\begin{frame}{Illustrative Example}
%We illustrate our approach with an example,
%extracted from the literature~\cite{Franklin15}.
%%
%We start with a candidate solution with all coefficients zero, $K=[0
%  \ 0 \ 0]^T$, and a precision of $I_p=13$, $F_p=3$.  In the first
%{\sc verify} stage, the {\sc safety} check finds the counterexample
%%
%$ x_0 = [-0.5 \ 0.5 \ 0.5] $.
%%
%After adding the new counterexample to its sets of {\sc inputs}, {\sc
%  synthesize} finds the candidate solution $K=[0 \ 0
%  \ 0.00048828125]^T$, which prompts the {\sc safety} verifier to
%return $x_0=[-0.5 -0.5 -0.5]$ as the new counterexample.
%
%In the subsequent iteration, the synthesizer is unable to find further 
%suitable candidates and it returns UNSAT, meaning that the current precision is
%insufficient.  Consequently, we increase the precision to $I_p=17$,
%$F_p=7$.
%%
%Since the previous counterexamples were obtained at lower precision,
%we remove them from the set of counterexamples.  Back in the {\sc
%  synthesize} phase, we re-start the process with a candidate solution
%with all coefficients $0$.  Next, the {\sc safety} verification stage
%provides the first counterexample at higher precision, $x_0=[-0.5
%  \ 0.5 \ 0.5]$ and {\sc synthesize} finds $K=[0 \ 0.01171875
%  \ 0.015625]^T$ as a candidate that eliminates this counterexample.
%However, this candidate triggers the counterexample
%$x_0=[0.5\ -0.5\ -0.5]$ found again by the {\sc safety} verification
%stage.  In the next iteration, we get the candidate $K=[0 \ 0
%  \ -0.015625]$, followed by the counterexample $x_0 = [0.5 \ 0.5
%  \ 0.5]$. Finally, {\sc synthesize} finds the candidate $K=[0.01171875
%  \ -0.013671875 \ -0.013671875]^T$, which is validated as a final
%solution by all verification stages.
%end{frame}

\begin{frame}[fragile]{Abstraction-based CEGIS}
\begin{figure}
\centering
{\scriptsize
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ 
   \&
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
   \& \node[fill=gray!20,align=center, minimum width=3.5cm] (verify) {\sc 3. verify ($\phi$)};
      \node[draw=none] (SAT) at ([xshift=2.2cm,yshift=-.3cm]verify)  {\sc PASS};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
  };
  \path
    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
    (abstract.south) edge node{$(\phi(K), k)$} (synth.north)
    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$(\phi(K),k)$} ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north)
    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
  \path[-] 
     (verify.north) edge node {$(k,x_0)$} (aux);
\end{tikzpicture}
}
\end{figure}
\end{frame}

\begin{frame}[fragile]{Abstraction-based CEGIS}
\begin{itemize}
\uncover<1->{ \item Calculate $\mat{T}$ such that $P_a = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}$ is the first line of $\mat{T}\mat{A}_b\mat{T}^{-1}$}
\uncover<2->{\item Calculate $N= \left \{ \nu_1+\nu_2+ \nu_3 \right \}$ from the quantizer resolutions and estimated round-off errors:

\begin{align*}
\nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] \wedge \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge \nu_3 \in \left[-q_3\ \ q_3\right]\nonumber
\end{align*}

where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is
the error introduced by the DAC and $q_3$ is the maximum truncation and
rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$}

\uncover<3->{
\item Calculate $\phi_\mathit{init}^K := -K x_0 \in \phi_{input} : x_0 \in \phi_{\mathit{init}}$}

\end{itemize}
\end{frame}

%
%\item In the {\sc synthesize} phase, we synthesize a candidate controller

%% Once we have established convergence, we may examine the 
%% safety specification $\phi_{safety}$.
%  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
%  $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver.
%%%   We obtain it by solving the SAT formula 
%%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
%%% that satisfies the input constraint and Jury's criteria for 
%%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
%%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
%If there is no candidate solution we return UNSAT and exit the loop.
